PoolTestRPaper

### 2020-06-18 paper/Paper.Rmd
Added a new simulation to the examples for the paper

>>>>

## Testing
A more realistic example:
- 3 regions with prevalence:
  - low (0.5%)
  - medium (2%)
  - high (4%) 
- 10 villages in each region with prevalence:
  - random normal distribted tight around region average, or 
  - one hotspot and one coldspot village
- 15 sites at each village.
  - Mosquitos caught at each site is random from normal/lognormal distribution so that 0 and 500 and both rare
  - Mosquitos pooled into test-tubes of 25 + one pool with remainder

```{r GenerateMoreRealisticDataset}
RegionPrevs <- c(A = 0.5, B = 2, C = 4)/100 #Prevalence in each region
NumRegions <- length(RegionPrevs)
NumVillages <- 10 #Villages per Region
NumSites <- 15 #Sites per village
MeanCatch <- 100; SDCatch <- 30 #Mean and SD of mosquito catch sizes
DispersionCatch <- 1.5
#expand.grid(1:NumSites,1:NumVillages,names(RegionPrevs))
#Catches <- data.frame(Catch = rnorm(NumRegions * NumVillages * NumSites, MeanCatch,sd = SDCatch))
Data <- data.frame()
for(R in names(RegionPrevs)){
  for(V in 1:NumVillages){
    VillageTruePrev <- 0
    while(VillageTruePrev<=0){
      VillageTruePrev <- rnorm(1,mean = RegionPrevs[[R]],sd = RegionPrevs[[R]]/5)
    }
    for(S in 1:NumSites){
      SiteTruePrev <- 0
      while(SiteTruePrev<=0){
        SiteTruePrev <- rnorm(1,mean = VillageTruePrev,sd = VillageTruePrev/5)
      }
      #Generate catch sizes from zero-truncated negative binomial distribution. 're-roll' sizes <= 0 to guarantee at least one mossie
      Catch <- 0
      while(Catch<=0){
        Catch <- rnbinom(1,mu = MeanCatch,DispersionCatch)
      }
      NumBigPools <- Catch %/% MaxPoolSize
      if(NumBigPools){
        Data <- rbind(Data,
                      data.frame(Region = R,
                                 Village = paste(R,V,sep = "-"),
                                 Site = paste(R,V,S,sep = "-"),
                                 PoolSize = rep(MaxPoolSize,NumBigPools),
                                 PrevalenceSite = SiteTruePrev,
                                 PrevalenceVillage = VillageTruePrev,
                                 PrevalenceRegion = RegionPrevs[[R]]))
      }
      SizeSmallPool <- Catch %% MaxPoolSize
      if(SizeSmallPool){
        Data <- rbind(Data,
                      data.frame(Region = R,
                                 Village = paste(R,V,sep = "-"),
                                 Site = paste(R,V,S,sep = "-"),
                                 PoolSize = SizeSmallPool,
                                 PrevalenceSite = SiteTruePrev,
                                 PrevalenceVillage = VillageTruePrev,
                                 PrevalenceRegion = RegionPrevs[[R]]))
      }

    }
  }
}
Data$Result <- with(Data,as.numeric(runif(nrow(Data)) < 1-(1-PrevalenceSite)^PoolSize))

PrevAll <- PoolPrev(Data,Result,PoolSize)
PrevRegion <- PoolPrev(Data,Result,PoolSize,Region)
PrevVillage <- PoolPrev(Data,Result,PoolSize,Region,Village)
PrevSite <- PoolPrev(Data,Result,PoolSize,Region,Village,Site)
